Combining information from photometric and spectroscopic data:\\ Don't waste your time in spectrophotometric calibration!

### 2014-08-07 tex/ms.tex
update figures for multiplicative models, add zoom in figure and add discussion text

\begin{figure*}[h!]
\includegraphics[width=\textwidth]{figures/sfig_b192-g242_020_cal.png}
\caption{Spectra resulting from draws from the posterior parameter
space conditioned on the calibrated \excluster~ spectrum and
photometry.  Left: For each of 5 draws from the posterior we show from
top to bottom, three components of the model: the mean cluster
spectrum, the calibration vector, and the mean prediction of $\Delta$
for the Gaussian process.  Right: From top to bottom, the full model
({\it cyan}) compared to the observed, calibrated spectrum ({\it
magenta}), the ratio of the observed to the modeled spectrum, and the
difference between the observed spectrum and the modeled spectrum
normalized by the uncertainty.
\label{fig:inferred_spectrum}}
\end{figure*}

@@

\begin{figure}[h!]
\includegraphics[width=0.5\textwidth]{figures/pfig_b192-g242_020_cal.png}
\caption{Model SEDs.  Top: The model photometric SED resulting from draws from the posterior
  parameter space conditioned ({\it cyan}) on the observed photometry
  ({\it magenta})  and spectra.  Bottom: uncertainty normalized
  residuals of the models from the observations. 
 . \label{fig:inferred_sed}}
\end{figure}

\begin{figure}[h!]
\includegraphics[width=0.5\textwidth]{figures/ptri_b192-g242_020_cal.png}
\caption{ Marginalized and joint PDFs of  subset of the physical
  parameters $\theta$ inferred from the spectophotometrically
  calibrated spectrum of \excluster. The blue lines indicate the
  parameter values that resulted from the powell minimization. \label{fig:inferred_params}}
\end{figure}

@@

\begin{figure*}[h!]
\includegraphics[width=\textwidth]{figures/cfig_b192-g242_020.png}
\caption{Left: Samples of the effective multiplicative calibration
  vector for the spectrophotometrically calibrated spectrum of
  \excluster~ ({\it cyan}) compared to that obtained from ancillary
  photometric data ({\it magenta}).  Right:  The same, but for the
  uncalibrated data. 
 \label{fig:inferred_calib}}
\end{figure*}

@@

We have demonstrated, using a sample of stellar clusters in M31, that
we can combine photometric and spectroscopic data in a principled way
to infer physical properties.  We do not resort to an arbitrary
down-weighting or up-weighting of certain data. Instead, we explicitly
model our uncertain knowledge of the spectral calibration and infer
this calibration jointly with the physical properties. For a number of
applications this combination of spectroscopy and photometry reduces
the need for spectrophotometric calibration.  Calibration information,
if it exists, can be incorporated into informative priors on the
calibration parameters of the model.

Our strategy is easily extensible to more complicated models, which
include for example night sky-line emission in the spectroscopy (or
residuals from an intial sky-line subtraction), and uncertainties in
wavelength calibration. {\color{blue} DISCUSS MORE COMPLICATED
COVARIANCE KERNELS, MULTIPLE KERNELS, etc.  MODEL CHECKING.}

In a heirarchical modelling context it should be possible to use the
inferred calibration parameters, along with additional information
about the observations (e.g. airmass, instrument temperature), to in
turn infer the parameters of a generative model for the
calibration. This generative model can then be used in the
(probabilistic) calibration of objects where the spectra are difficult
to model explicitly.

Limitations.  The strategy we have advocated has several limitations.
First, it requires a generative model for the spectrum of the object
of interest, and is thus ill-suited to discovery projects.  Second,
care must be taken to avoid absorbing interesting model deficiencies
into the calibration model.  Third, we have made the assumption that
the spectroscopy and the photometry are sampling the same populations.
In practice, differences between spectroscopic and photometric
apertures often mean that the photometry and the spectroscopy are sampling
slightly different physical regions.  The correct response to this
situation is to explicitly model the differences, incorporating prior
information about the spatial variation of physical properties.
Finally, this method is computationally intensive and expensive, since
we are constantly inverting largish matrices.

>>>>

\begin{figure*}[h!]
\includegraphics[width=\textwidth]{figures/sfig_b192-g242_225_cal.png}
\caption{Spectra resulting from draws from the posterior parameter
space conditioned on the calibrated \excluster~ spectrum and
photometry.  Left: For each of 5 draws from the posterior we show from
top to bottom, three components of the model: the mean cluster
spectrum, the calibration vector, and the mean prediction of $\Delta$
for the Gaussian process.  Right: From top to bottom, the full model
({\it cyan}) compared to the observed, calibrated spectrum ({\it
magenta}), the ratio of the observed to the modeled spectrum, and the
difference between the observed spectrum and the modeled spectrum
normalized by the uncertainty.
\label{fig:inferred_spectrum}}
\end{figure*}

\begin{figure*}[h!]
\includegraphics[width=\textwidth]{figures/zfig_b192-g242_225_cal.png}
\caption{Zoom-in on selected regions of the observed spectrum, showing
also draws from the posterior model for the spectra in these regions
and residulas of these draws from the observations.
\label{fig:zoom_spectrum}}
\end{figure*}

@@

\begin{figure}[h!]
\includegraphics[width=0.5\textwidth]{figures/pfig_b192-g242_225_cal.png}
\caption{ Model SEDs.  Top: The model photometric SED resulting from
draws from the posterior parameter space conditioned ({\it cyan}) on
the observed photometry ({\it magenta}) and spectra.  Bottom:
uncertainty normalized residuals of the models from the observations.
\label{fig:inferred_sed}}
\end{figure}

\begin{figure}[h!]
\includegraphics[width=0.5\textwidth]{figures/ptri_b192-g242_225_cal.png}
\caption{ Marginalized and joint PDFs of subset of the physical
parameters $\theta$ inferred from the spectophotometrically calibrated
spectrum of \excluster. The blue lines indicate the parameter values
that resulted from the powell minimization.
\label{fig:inferred_params}}
\end{figure}

@@

\begin{figure*}[h!]
\includegraphics[width=\textwidth]{figures/cfig_b192-g242_225.png}
\caption{Left: Samples of the effective multiplicative calibration
vector for the spectrophotometrically calibrated spectrum of
\excluster~ ({\it cyan}) compared to that obtained from ancillary
photometric data ({\it magenta}).  
%Right: The same, but for the uncalibrated data.
 \label{fig:inferred_calib}}
\end{figure*}

@@

We have demonstrated, using a sample of stellar clusters in M31, that
we can combine photometric and spectroscopic data in a principled way
to infer physical properties.  We do not resort to an arbitrary
down-weighting or up-weighting of certain data. Instead, we explicitly
model our uncertain knowledge of the spectral calibration and infer
this calibration jointly with the physical properties. For a number of
applications this combination of spectroscopy and photometry reduces
the need for spectrophotometric calibration, such that the less
expensive photometry is sufficient.  Additional calibration
information, if it exists, can be incorporated into informative priors
on the calibration parameters of the model, or inform the construction
of the calibration model.

Our strategy is easily extensible to more complicated models, which
include for example night sky-line emission in the spectroscopy (or
residuals from an intial sky-line subtraction), and uncertainties in
wavelength calibration. Furthermore, more complex physical models may
be considered for the mean object model, for example including SFH
parameters so as to model galaxies.  {\color{blue} DISCUSS MORE
COMPLICATED COVARIANCE KERNELS, MULTIPLE KERNELS, etc.  MODEL
CHECKING.}

In a heirarchical modelling context it should be possible to use the
inferred calibration parameters, along with additional information
about the observations (e.g. airmass, instrument temperature), to in
turn infer the parameters of a generative model for the calibration
\citep[e.g.][]{spectrophot}. This generative model can then be used in
the (probabilistic) calibration of objects where the spectra are
difficult to model explicitly.

Limitations.  The strategy we have advocated has several limitations.
First, it requires a generative model for the spectrum of the object
of interest, and is thus ill-suited to discovery projects.  Second,
care must be taken to avoid absorbing interesting model deficiencies
into the calibration model. For example, in the model we have
described, it is possible that broad shallow features (for example due
to molecular bands or absorption line complexes) will be absorbed into
the Gaussian process. Third, we have made the assumption that the
spectroscopy and the photometry are sampling the same populations.  In
practice, differences between spectroscopic and photometric apertures
often mean that the photometry and the spectroscopy are sampling
slightly different physical regions.  The correct response to this
situation is to explicitly model the differences, incorporating prior
information about the spatial variation of physical properties.
Finally, this method is computationally intensive and expensive, since
we are constantly inverting largish matrices.

Fundamentally, calibration involves observing a `known' or `truth'
with an instrument, and using the observation to infer the effects of
the instrument.  However, we do not have knowledge of a single truth
for any object, only relative probabilities for what might be true.
In this sense, one should never use a single point estimate of the
calibration, the full distribution of the possible calibrations should
be inferred from our probabilistic knowledge of the calibration object
and forward propogated \citep[e.g.][]{lee11}. Once this is done, the only the
only distinction between 'calibration' objects and targets of interest
is the complexity of the model for the object and the level of
uncertainty in the calibration object spectrum.  If one is interested
in inferring parameters of interest of spectral models of
astrophysical objects, then there is no reason not to use those
objects themselves as calibration objects.
